Manuscript title here

### 2024-09-14 manuscript.Rmd
nått ord här och där, inga större skillnad

@@

We conducted a registry based retrospective cohort study, using data from the trauma registry and trauma care quality database at the Karolinska University Hospital in Solna. We then linked the two databases to assess what types of OFI occurred in patients arriving in shock and use adjusted logistic regression to assess the association between the degree of shock and odds of opportunities for improvement.

>>>>

Infoga OFI del och koppla samman

@@

We conducted a registry based retrospective cohort study, using data from the trauma registry and trauma care quality database at the Karolinska University Hospital in Solna. We then linked the two databases to first assess what types of OFI occurred in patients arriving in shock and then use adjusted logistic regression to assess the association between the degree of shock and odds of opportunities for improvement.
